### 2017-10-14 Gruba/07-rela.tex

With respect to feature analysis, there have been existed works of mining users' info, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
Our work, however, does not focus on the mining process per se; we use the mined info as the input for user clustering and group modeling.

@@

There have been established work of extracting user interests.
\cite{IEEEexample:journals/fcsc/LiuCS12} mined the user interests by exploring keywords of microblogs with the aid of word frequency and machine translation.
\cite{IEEEexample:conf/webi/XuLXY11} proposed a method of extending the topic model to obtain use interests.
Also, \cite{IEEEexample:conf/and/MichelsonM10} used a knowledge base and \cite{IEEEexample:conf/icde/FengW14} provided a solution of using hashtag for interest analysis.
\cite{IEEEexample:conf/wikis/LimD13} summarized user interest by exploring the mentioned celebrities;
Similarly, \cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} leveraged the followed experts to result interest characteristics.
Unlike the existed solutions, \sys{} employs a cell lexicon to properly express user interest in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF are employed.

Approaches of grouping users in social network could fall into a variety of categories.
\cite{IEEEexample:conf/icwsm/PennacchiottiP11} grouped users by the info of race, political view and etc.
\cite{IEEEexample:journals/tkdd/ZhangCFLYZY17} studied the social groups on Facebook and Wechat, resulting various patterns of group evolution.
\cite{IEEEexample:conf/aaai/WangDNGEB16} proposed a time-varying factor to measure the affinity between users and groups such that proper group proposals are recommended.
More recent studies also look into mining user communities.
\cite{IEEEexample:conf/wsdm/YangL13} employed matrix decomposition to mine user community;
\cite{IEEEexample:conf/www/RuanFP13} and \cite{IEEEexample:he2014overlapping} considered followees info for user clustering;
\cite{IEEEexample:conf/aaai/ShiokawaFO13} proposed an incremental algorithm to mine user community using modular degree as the clustering yardstick.
Providing the diversity of user features, \sys{} employs feature of info, behavior and interest into user clustering.

>>>>

With respect to feature analysis, there have been existing work of mining user features, such as race \cite{IEEEexample:conf/icwsm/PennacchiottiP11}, gender \cite{IEEEexample:conf/emnlp/CiotSR13}, age \cite{IEEEexample:conf/icde/ParkHHL09}, political preference \cite{IEEEexample:conf/icwsm/PennacchiottiP11,IEEEexample:conf/acl/VolkovaCD14,IEEEexample:kosinski2013private} and occupation \cite{IEEEexample:journals/tmm/FangSXH15,IEEEexample:conf/icde/FanCTWC16}.
Our work, however, does not focus on the mining process per se; we use the mined features as the input for user clustering and group based behavior modeling.

@@

There have been established work of extracting user interests.
\cite{IEEEexample:journals/fcsc/LiuCS12} mined the user interests by exploring keywords of microblogs with the aid of word frequency and machine translation.
\cite{IEEEexample:conf/webi/XuLXY11} proposed a method of extending the topic model to obtain use interests.
Also, \cite{IEEEexample:conf/and/MichelsonM10} used a knowledge base and \cite{IEEEexample:conf/icde/FengW14} provided a solution of using hashtag for interest analysis.
\cite{IEEEexample:conf/wikis/LimD13} summarized user interest by exploring the mentioned celebrities;
Similarly, \cite{IEEEexample:conf/recsys/BhattacharyaZGGG14} leveraged the followed experts to result interest characteristics.
Different from these existing solutions, \sys{} employs a cell lexicon to properly express user interests, in which Twitter-LDA \cite{IEEEexample:zhao2011comparing} and TF-IDF are employed.

Approaches of grouping users in social networks could fall into a variety of categories.
\cite{IEEEexample:conf/icwsm/PennacchiottiP11} grouped users by the info of race, political view and etc.
\cite{IEEEexample:journals/tkdd/ZhangCFLYZY17} studied the social groups on Facebook and Wechat, resulting various patterns of group evolution.
\cite{IEEEexample:conf/aaai/WangDNGEB16} proposed a time-varying factor to measure the affinity between users and groups such that proper group proposals are recommended.
More recent studies also look into mining user communities.
\cite{IEEEexample:conf/wsdm/YangL13} employed matrix decomposition to mine user community;
\cite{IEEEexample:conf/www/RuanFP13} and \cite{IEEEexample:he2014overlapping} considered followees info for user clustering;
\cite{IEEEexample:conf/aaai/ShiokawaFO13} proposed an incremental algorithm to mine user community using modular degree as the clustering yardstick.
Providing the diversity of user features, \sys{} employs basic, behavior and interest features into user clustering.
